---
title: "Intro to data visualization using ggplot2"
---

1.  The grammar of graphics
2.  Datasets and mapping
3.  Geometries
4.  Statistical transformation and plotting distribution
5.  Position adjustment and scales
6.  Coordinates and themes
7.  Facets and custom plots

<a href="https://econ147-special-topic.github.io/econ147-lecture/module-intro-ggplot" target="_blank" class="btn-slides">View slides in new window</a>

::: {.box style="padding-bottom:56.25%; position:relative; display:block; width: 100%"}
<iframe width="100%" height="100%" src="https://econ147-special-topic.github.io/econ147-lecture/module-intro-ggplot" frameborder="0" allowfullscreen style="position:absolute; top:0; left: 0">

</iframe>
:::

#### Presentation keyboard shortcuts

::: text-line-space
<ul>

<li>Use <kbd>←</kbd> and <kbd>→</kbd> to navigate through the slides</li>

<li>Use <kbd>F</kbd> to toggle full screen</li>

<li>Use <kbd>O</kbd> to view an overview of all slides</li>

<li>Use <kbd>?</kbd> to see a list of other shortcuts</li>

</ul>
:::

#### Line plot: baby names

```{r}
#| warning: false
#| comment: false
#| fig-width: 15
#| fig-height: 10

# libraries
library(tidyverse)
library(babynames)

friends <- babynames %>% 
  filter(year >= 1950,
         name %in% c("Christopher", "Dave", "Karl"),
         sex == "M")

ggplot(data = friends,
       mapping = aes(x = year, y = n, color = name)) +
  geom_line(linetype = "dashed") +
  geom_point(size = 4, alpha = 0.5) +
  scale_y_log10() +
  theme_minimal() +
  theme(axis.title = element_text(size = 24),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 18)
        )

```


#### Scatter plot: mpg dataset

```{r}
#| warning: false
#| comment: false
#| fig-width: 15
#| fig-height: 10

mean_hwy_data <- mpg %>% 
  group_by(class) %>% 
  summarise(mean_hwy = mean(hwy, na.rm = TRUE))

ggplot(data = mpg,
       mapping = aes(x = class, y = hwy, color = class)) +
  geom_point(position = "jitter", size = 3, alpha = 0.5) +
  geom_point(data = mean_hwy_data, aes(y = mean_hwy), size = 7) +
  labs(title = "Fuel consumption per class vehicle",
       x = "Class of vehicle",
       y = "Highway fuel consumption") +
  theme_minimal() +
  theme(plot.title = element_text(size = 24),
        axis.title = element_text(size = 24),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 18)
        )

```












